\plaintitle

### 2018-04-03 paper/paper.tex
...

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}

@@

  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  \textsf{ExpandHelp} that can be used in a wide area of situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \texttt{git} commands
  from fragments of users' intentions.

@@

@@

\section{Example}

We have implemented the \textsf{GitHtlp} system
with which a user can translate his vague intention in various languages
into a complete \texttt{git} commands
using the \textsf{ExpandHelp} framework.

\paragraph{Entering a command}

@@

\begin{figure}[b]
  \includegraphics[width=8cm,bb=0 0 670 254]{figures/bash1.png}
  \caption{Bash shell.}
  \label{bash1}
\end{figure}

@@

\begin{quotation}
  \begin{verbatim}
    $ git diff README.md
    $
  \end{verbatim}
\end{quotation}

Nothing happens, because this is not the right command
to compare the latest version with one of the older versions.
%
More experienced user might use a command like the following,
but it does not show anything either, because the version specification
``\verb|HEAD^^|''
points at a file included in the older ``commit'',
and

@@

If {\GH} is installed,
the user can type a special key (e.g. \texttt{Cmd-Ctrl-G}) to invoke {\GH}
after typing ``\texttt{git RE 2}''.

\begin{figure}[b]
  \includegraphics[width=8cm,bb=0 0 1290 866]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says ``.....'',
which means that ``to compare README with two older verson.''
%
If the user thinks that that's what he wanted to do,
he can select the entry by typing arrow keys and
type the enter key.
Then the command line is replaced by the correct command string
that satisfies the user's need.

A description like ``2日前''(2 days ago) was also shown in the candidate list.
This means that the user can use the same string ``\tettt{git RE 2}''
for getting the README.md file of the day before yesterday.
The command is ``$ git ... '@{2 days ago}''.
Although such command options are very difficult to remember,
users can do the same thing only by saying RE and 2.

@@

\subsection{IME}

Text input systems for various languages are used widely in the world.
They are called ``????''

There are many

\subsection{Command line completion}

% コマンドライン補完
% Emacs的な古いやつ、PBEのやつ、学習するやつ

% Gitのcompletion

@@

@@

@@

@@

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{sample}

>>>>

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{``\texttt{#1}''}

@@

  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in a wide area of situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \texttt{git} commands
  from fragments of users' intentions.

@@

Online help systems are usually hard to use because of the
vocabulary problem \cite{Furnas:1987:VPH:32206.32212}.

People don't use online help
\cite{Novick:2006:WDP:1166324.1166329}.

@@

\section{Example: GitHelp}

We implemented the {\GH} system
with which a user can translate his vague intention in various languages
into a complete \texttt{git} command
using the {\EH} framework.

\subsection{Entering a command}

@@

% \begin{figure}[h]
%   \includegraphics[width=8cm,bb=0 0 670 254]{figures/bash1.png}
%   \caption{Bash shell.}
%   \label{bash1}
% \end{figure}

@@

\begin{quotation}
  \begin{verbatim}
    $ git diff README.md
    $ xxx
  \end{verbatim}
\end{quotation}

Nothing happens, because this is not the approriate command
to compare the latest version of \texttt{README.md}
with older versions.
%
More experienced user might use a command like the following,
but it does not show anything either, because the version specification
``\verb|HEAD^^|''
specifies a file included in the older ``commit'',
and the following command only compares the \texttt{README.md}
with the with the file included in the last commit, where
\texttt{README.md} might be the same as the latest version.

@@

If {\GH} is installed,
the user can type a special key (e.g. \texttt{Cmd-Ctrl-G}) to invoke {\GH}
after typing ``\verb|git RE |'' to see how he can do the job.

\begin{figure}[h]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  \includegraphics[width=10cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash1}
\end{figure}

Here, various candidate entries with
descriptios and command strings are listed.
One of the entries says ``README.mdをひとつ前のバージョンと比較する'',
which means that ``to compare README with the last verson.''
%
If the user thinks that that's what he wanted to do,
he can select the entry by moving the selection by typing arrow keys
and type the enter key.
Then the command line is replaced by the correct command string
that satisfies the user's need.

A description like ``1日前''(1 day ago) was also shown in the candidate list.
This means that the user can use the same string ``\texttt{git RE 1}''
for getting the README.md file of the day before yesterday.
The command is ``\verb|$ git ... '@{1 days ago}|''.
Although such command options are very difficult to remember,
users can do the same thing only by saying \texttt{RE} and \texttt{1}.

@@

\subsection{Input Methods}

Text input systems for non-English languages are used widely in the world, and
they are called as ``input methods'' (IMs).

\begin{figure}[b]
  \includegraphics[width=8cm,bb=0 0 976 670]{figures/nyuuryoku-ime.png}
  \caption{Example IM for Japanese text input.}
  \label{bash1}
\end{figure}

Many research and development on IMs have been performed for years, and
people are using them all the time for entering text in their mother language.

IMs are a kind of translation system that convert one
expression (pronunciation, etc.) into a textual form of a language.
In the above example, ``kanji'' will be translated to ``漢字''.

IMs are very popular especially in South-East Asian countries, and
it is very common for people there to 
use translation systems for using computers.

\subsection{Text and code completion}

On text editors an│shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \tt{la} on the Unix shell,
\tt{latex}, \tt{latex}, and other commands are shown as candidates.
When a user types \tt{ls RE} and types the TAB key,
Unix shell checks the directory, find the \texttt{README.md} file, and
replace the user's input with \tt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been adopted in text editors and command line editors.

User's history data can be used for 
The Reactive Keyboard system\cite{ReactiveKeyboard}
accumlates the user's command history and use the data
for predicting the user's next command.
Programing-by-Example (PBE) systems\cite{Cypher}\cite{Lieberman}.

Gitsome(https://github.com/donnemartin/gitsome)
helps \texttt{git} users by
showing possible arguments and manuals on the Unix shell,
just like {\GH}.
The direction is alomost the same as {\GH}, but
Gitsome does not support .....

@@

Many smart IDEs for suggesting codes are proposed.

賢い補完
\cite{Little:2006:TKC:1166253.1166275}
% キーワードの羅列からコマンドを作成するという考えはとても正しいと思うが、実装がいかがなものか?
% キーワードぐらいは思い出せるプログラマが対象になっている
% 「margin」とか「left」とかいう単語は思い出す必要がある
% 「ちょっと字下げ」とか言っても駄目
% キーワードが違ってると駄目?
% いろいろズルをしてるようだ
% [[ActiveDocument]]はよく出てくるので特別扱いしているとか
% ステミングをしている
% ``the'' ``to'' などは捨ててるのだろう
% そもそもリカーシブな検索アルゴリズムにかなり無理がありそう
% テンプレートを作るのは大変ではないのか?

AnyCode\cite{Gvero:2015:SJE:2814270.2814295}
% [anyCode]というシステム。自然言語キーワードを入力するとコードスニペットが表示される。
% [[copy fileA fileB]]みたいなキーワードから[[FileUtil.copyFile(new File(fileA), new File(fileB))]]みたいなコード候補を生成する
% [自然言語処理]を行なっている
% [https://github.com/tihomirg/nlpcoder/tree/noola GitHub]
% 曖昧検索はできない
% 真面目に自然言語を入れる必要がある
% `123`みたいなパラメタは使えるか?
% 使えると思うが例には出てこない
% コードの説明文は出ない?
% FileUtil.copyFile(new File(fileA), new File(fileB)) と言われても、どちらが新しいファイルなのかわからない

Active Code Completion\cite{Omar:2012:ACC:2337223.2337324}
% [/ palette] と呼ばれるテンプレートを用意して[IDE]でのコード補完をサポートする
% `getDefaultColor()` を定義したいとき`purple`と入力すると、それに対応した候補が提示されるとか
% 普段使ってる環境で有益な候補が表示されると嬉しいだろうと言っている
% [[コメント]]
% [Jun Kato.icon]
% > Active code completionも思い出しました。型ごとに適した入力インタフェースを出すコード補完インタフェースのnn提案です。確か。
% [増井俊之.icon]
% IDEでどういう機能が欲しいかサーベイして設計したことになっている
% 色選択と正規表現のためのコード生成をサポートした例が紹介されている
% 一般的な補完コマンド起動によって呼び出されるようだ
% サポートウィンドウはHTML5で生成する
% しかし両者とも[/palette]の作成はかなり大変である
% 普通のユーザが作れるようなものではない
% [* 作成がすごく大変]で、[* 特定のIDEでしか使えない]という問題があると思う

Code Completion from Abbreviated\cite{Han:2009:CCA:1747491.1747530}
% [HMM]を使って正しいコードを予測して提示する
% `ch opn`みたいなテキトーな入力から`chooser.showOpenDialog()`みたいな正しいコードが候補に出る
% コードデータベースを解析
% [[コメント]]
% [増井俊之.icon] 2018/3/23 18:53
% コードのほんの一部を指定すると正しく予測されるというのは面白い
% HMMってそういうのに使えるのね
% しかし[* 関数名とか全然覚えていないときは使えないだろう]
% [語彙問題]が解決できてない
% だとすると高速入力の役にはたつが、何もかもわからない人をサポートはできない
% 用例データが存在しない場合も使えない
% [IDE]でしか使えない
% [Cyrus Omar: Active code completion]で参照されている

@@

\subsection{Context-based help}

@@

BluePrint \cite{Brandt:2010:EPI:1753326.1753402}
%   サンプルコードをすぐ参照して利用できる[IDE]

Bjorn\cite{Hartmann:2010:OPS:1753326.1753478}
% 他人のヒストリを使ってコンパイルエラー対処法をサジェスト

@@

参考文献にすることはないか

Jupyter
Eve

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{paper}
